\documentclass[11pt,]{resume}
\usepackage{ebgaramond}
\usepackage{filemod}
\usepackage[dvipsnames]{xcolor}
\definecolor{grey}{gray}{0.1}
\name{Robin Joshi}
\address{Dallas-Fort Worth metroplex, TX}
\address{(xxx)~$\cdot$~xxx~$\cdot$~xxxx \\ robin****@****.com}
\address{\textcolor{gray}{last updated:} \filemodprintdate{\jobname}}

\begin{document}
	\begin{rSection}{Education}
		\textbf{Southeastern Louisiana University} \hfill{August 2012 - December 2015} \\ B.S. in Mathematics and Computer Science (one degree)
	\end{rSection}

	\begin{rSection}{Experience}
		\begin{rSubsection}{JPM Chase & Co.}{February 2024 - Present} {Associate SWE III}{Birmingham, AL}
			\item ...
		\end{rSubsection}

		\begin{rSubsection}{Walmart Global Tech}{October 2021 - September 2022}{Software Engineer via Kitestring Technical Services}{Birmingham, AL}
			\item Maintained backend apis for inventory management of COVID-19 vials.
			\item Worked on microservices in the Health and Wellness space to assist Pharmacists in drug dispensation.
			\item Created POCs and took part in planning and designing of rx related apis for a Pharmacy application.
			\item Worked on root cause analysis of several production issues for COVID-19 scheduler application.
		\end{rSubsection}

		\begin{rSubsection}{BBVA, Now part of PNC }{April 2018 - December 2020}{Software Developer via Apex Systems}{Birmingham, AL}
			\item Maintained BBVA's customer facing application for Credit/Loans as a full-stack engineer.
			\item Collaborated with domain experts for estimating and planning features.
			\item Collaborated with various internal and external teams and implemented several features.
			\item Worked on several critical production issues, both on ui and backend integration layer.
			\item Integrated backend services with legacy systems.
		\end{rSubsection}

		\begin{rSubsection}{BBVA, Now part of PNC }{October 2017 - March 2018}{Software Developer via Cubic Technologies}{Birmingham, AL}
			\item[]\vspace{-1.5\baselineskip}
		\end{rSubsection}
	\end{rSection}

	\begin{rSection}{Working knowledge of}
		\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
			Languages & Java, kotlin, JavaScript, Python, Scala  \\
			Frameworks \& APIs & Spring Boot, Spring Cloud, ktor, Apache Kafka \\
			Containers and Cloud & docker, k8s, AWS, OpenTelemetry \\
			Utilities \& Tools & Maven, Gradle, Git \\
			Databases & MySQL, Cosmos, Cassandra, Oracle \\
			CI CD & GithubActions, TravisCI, Jenkins
			APM Dynatrace, Splunk
		\end{tabular}
	\end{rSection}
\end{document}
